A Meta-analysis of Fungicide Spray Schedules to Minimise Yield Loss from Powdery Mildew in Australian Mungbean

### 2020-08-07 paper/paper.Rmd
Add FAIR to list of abbreviations

## Trial Criteria for Inclusion and Description

The data for this study were obtained through studies that were conducted by the authors, FAIR (Findable, Accessible, Interoperable, Reusable) data available from GRDC Online Farm Trials <https://www.farmtrials.com.au/><!--Technically we did not use data from this location we obtained it from Lawrie Price-->, personal correspondence with colleagues and collaborating institutions.
Trial data were obtained in different formats with varying levels of information.
Raw data was obtained for some trials, others reported only the means of each treatment, with all but two trials reporting some form of variance along with the mean.
In total, 26 trials were collated.

>>>>

## Criteria for Trial Data Inclusion

The data for this study were obtained through studies that were conducted by the authors, data that were the intellectual property of the University of Southern Queensland, and through personal correspondence.
Trial data were obtained in different formats with varying levels of information.
Raw data was obtained for some trials, others reported only the means of each treatment, with all but two trials reporting some form of variance along with the mean.
In total, 26 trials were collated.
